---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# condor

The goal of condor is to ...

## Installation

You can install condor from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("yuliasidi/condor")
```

# Using ssh package to interact with uconn cluster

load library
```{r}
library(ssh)
```

## create ssh connection to cluster

```{r}

session <- ssh_connect(Sys.getenv('UCONN_USER'))

```

## Transfering files to and from cluster

Example: path to a file

```{r}

file_path <- R.home("COPYING")

file_path

```
 
local   ==> cluster
```{r}

scp_upload(session, file_path)

```
 
cluster ==> local
```{r}

scp_download(session, "COPYING", to = tempdir())

```

check that the file passed back and forth is the still the same

```{r}

c(
  tools::md5sum(file_path),
  tools::md5sum(file.path(tempdir(), "COPYING"))
  )

```

# Running commands from local on the cluster

commands to run

```{r}

cmds <- c(
  'ls jobs/cluster', # list files in jobs cluster
  'cd jobs/cluster', # move to jobs/cluster
  'cat Rcalcpi.condor' # print the lines of Rcalcpi.condor
)

```

Run without returning anything to local R  

```{r remedy001}

ssh_exec_wait(session, command = cmds)

```

Capturing the output from the cluster terminal as a list object in the local `R`

```{r remedy002}

out <- ssh_exec_internal(session, command = cmds)

```
 
status of the lines that were run 
 
```{r}

out$status # 0 means everything was run ok

```

## Printing the contents of out

using `ssh_print`
 
```{r}

condor::ssh_print(out$stdout)

```

# close ssh connection to cluster

```{r remedy004}
      
ssh_disconnect(session)

```
  
